---
title: "Nasta Durand's Website"
---

Hello world, welcome to my page! I'm Nastassjia Durand. I'm a graduate student at Baruch College. Business Analytics major, with a concentration in Data Analytics. I've been working for 5+ years in project management, consulting and strategy, across financial services (PwC, BNP Paribas, Allianz), digital innovation and sustainability.

To complete this experience and start transitioning to data analytics, I did an internship this summer at the MTA, within the LIRR Strategic Priorities team (Office of the President). The role blended strategy with data insights, to make strategic recommendations based on tangible internal data. I extracted, processed (cleaned), analyzed and translated data into actionable insights for leadership. This experience represented my first concrete experience in my project to transition into data analytics.

My goal is simple and straightforward  - I want to become a kind of "hybrid", who can both speak technical and non-technical. I started in business, and now I aim to add the technical layer to drive transformation based on real information. I strongly believe that AI can allow us to be more efficient and productive, not by replacing us but working with it (being an expert before using the tool). This is where learning how to manipulate data and how to use the technology can be beneficial.

Projects include: 

- NYPD crime dataset analysis - from importing with API, cleaning, analyzing, to exporting to a database (Baruch coursework) - Python, pandas, SQLite

- DBMS deployment - from business requirements to front-end app for business usage (Baruch coursework) - MySQL, Flask

- GenAI HR screening tool - generate a tool using AI projects to shortlist candidates for a role (Baruch coursework) - LLM

- Rider verbatim analysis - cleaned and analyzed ~17,000 rider verbatim using Python (pandas), scikit-learn, and NLP; built branch-level insight dashboards (qualitative and quantitative), delivered recommendations to leadership (MTA experience)

- Infrastructure fund/transaction benchmarking - analyzed 20+ infrastructure funds and 500+ transactions to analyze specific market positioning of interest to the team, and identify shifts in priorities (BNP Paribas experience)

[View my resume](https://drive.google.com/file/d/1dnv0r7P2SC_PIpQ0gcT9UW98lH2Nr4CN/view?usp=sharing)

```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "Here's my school, <b>Baruch College</b>!")
```

