---
title: "Nasta Durand's Website"
---

My name is Nastassjia Durand. I'm a current graduate student at Baruch College, studying Business Analytics, with a concentration in Data Analytics. 

My background spans project management and consulting (PwC France), with experience across financial services (BNP Paribas New York, Allianz France), digital innovation and sustainability. 

I've recently interned this summer 2026 in New York with the Strategic Priorities team at the MTA Long Island Rail Road, at the Office of the President. I collaborated closely with the team to contribute to the LIRR’s strategic initiatives by translating data into clear insights for leadership review. I’ve gained hands-on experience in public sector strategy and transportation operations. 

My goal is to become a hybrid professional, who speaks both technical and non-technical. Leveraging my background in consulting, and adding the technical layer to drive transformation.

Projects include: 

- End-to-end dataset analysis (Baruch coursework) - Python, pandas, SQLite

- Full-cycle DBMS built from business requirements to deployment (Baruch coursework) - MySQL, Flask

- GenAI HR screening tool for candidate shortlisting (Baruch coursework) - LLM

- Rider verbatim analysis at LIRR/MTA - cleaned and analyzed ~17,000 rider verbatim using Python (pandas), scikit-learn, and NLP; built branch-level insight dashboards (qualitative and quantitative), delivered recommendations to leadership

- Peer railroad benchmarking research at LIRR/MTA - benchmarked domestic and international railroads across 4 dimensions to shortlist improvement initiatives

- Infrastructure fund/transaction benchmarking at BNP Paribas - analyzed 20+ infrastructure funds and 500+ transactions to inform market positioning

[View my resume](https://drive.google.com/file/d/1dnv0r7P2SC_PIpQ0gcT9UW98lH2Nr4CN/view?usp=sharing)

```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "Here's my school, <b>Baruch College</b>!")
```

