---
title: "STA 9750 Mini-Project #01: What We Watched: Exploring Netflix Viewing Data"
author: "Nastassjia Durand"
date: "2026-09-27"
format:
  html:
    code-fold: true
    toc: true
---

```{r}
#| label: setup
#| message: false
#| echo: false
library(tidyverse)
library(skimr)
library(gt)
```

***What is the Netflix What We Watched Report?***

- Netflix What We Watched Report - published every 6 months starting in 2023
- The "WWW" reports aggregate total global viewership for almost the entire Netflix catalog over six months periods
- The data is acquired to analyze viewership to make strategic decisions on the 2027 budget

### Step 1/ Data Ingest and Cleaning

**Goal**: ingest and clean the data to make it efficiently usable for analysis.

**Steps**: read, load the data into R and transform it.

1. Ingest the data using the `load_netflix_data()` function
2. Examine the data using the `View(NETFLIX_DATA)` feature
3. Fix column titles by adding a `rename()` step in the original acquisition code
4. Fix column types by adding a `mutate()` step in the original acquisition code 

*Note 1*: the following column titles were identified for the `rename()` cleaning process: `Title` - capital letter, `Runtime` - capital letter, `Views` - capital letter, `Hours Viewed`	- capitals and a space, `Release Date`	- capitals and a space and `Available Globally?` - capitals, a space, and a ?

*Note 2*: the following column titles were identified for the `mutate()` cleaning process: `year` - from `chr` to `int` and `available_globally` - from `chr` to `lgl`

Inspect the code by clicking on the drop-down menu below:
```{r}
#| label: load-data
#| message: false
#| warning: false
#' Acquire Netflix What We Watched Reports
#' 
#' This function will acquire and standardize all data for MP#01
#' from Netflix. Because Netflix hosts the data files behind a CDN, we
#' are accessing the release pages and automatically extracting links to the
#' relevant files (with CDN hash). 
#' 
#' After import, files are stacked vertically and some basic cleaning is
#' performed. 


load_netflix_data <- function(){
  # Note to students: Make sure you have installed the tidyverse and fs packages
  #                   before beginning this assignment. If you aren't sure,
  #                   simply run `library(tidyverse)` at your R Console and, if
  #                   you don't see an error message, `tidyverse` has been 
  #                   installed. (Same for `fs`) If you still need to install
  #                   either package, use the `install.packages` function as 
  #                   demonstrated in class.
  library(tidyverse)
  library(rvest)
  library(readxl)
  library(fs)

  data_dir <- path("data", "mp01")
    
  if(!dir_exists(data_dir)){
    dir_create(data_dir, showWarnings=FALSE, recurse=TRUE)
  }
  
  NETFLIX_URLS <- list(
    `2023H1` = "https://about.netflix.com/news/what-we-watched-a-netflix-engagement-report",
    `2023H2` = "https://about.netflix.com/news/what-we-watched-the-second-half-of-2023",
    `2024H1` = "https://about.netflix.com/news/what-we-watched-the-first-half-of-2024",
    `2024H2` = "https://about.netflix.com/news/what-we-watched-the-second-half-of-2024",
    `2025H1` = "https://about.netflix.com/news/what-we-watched-the-first-half-of-2025",
    `2025H2` = "https://about.netflix.com/news/what-we-watched-the-second-half-of-2025",
    `2026H1` = "https://about.netflix.com/news/what-we-watched-the-first-half-of-2026"
  )
  
  download_if_needed <- function(url, local){
    if(!file_exists(local)){
      download.file(url, local, quiet = TRUE, mode = "wb")
    }
    
    return(local)
  }
    
  NETFLIX_URLS |> 
    map(read_html) |> 
    map(html_element, xpath = "//a[contains(@href, '.xlsx')]") |> 
    map_chr(html_attr, "href") |> 
    enframe("period", "url") |> 
   mutate(path = path(data_dir, paste0(period, ".xlsx")), 
          path = map2(url, path, download_if_needed), 
          data = map(path, read_excel, skip=3, na="*"), 
          data = map(data, \(x) x |> mutate(`Release Date` = as.Date(`Release Date`)))) |>
    unnest(data) |> 
    select(-url, -path) |> 
    mutate(year=str_sub(period, 1, 4), 
           half=str_sub(period, start=6), 
           period_start = make_date(year, if_else(half==1, 1, 7), 1), 
           period_end = make_date(year, if_else(half==1, 7, 12), if_else(half==1, 30, 31))) |> 
    filter(!is.na(`Hours Viewed`)) |> 
    mutate(live_event = !is.na(Runtime) & str_detect(Runtime, "\\d+:\\d+\\*"), 
           clean_time = str_remove(Runtime, fixed("*")),
           Runtime = 60 * hour(hm(clean_time)) + minute(hm(clean_time))) |>
    select(-clean_time) |>
    mutate(Runtime = coalesce(Runtime, mean(Runtime, na.rm=TRUE)), 
           .by=Title, 
           Title = stringi::stri_trans_general(Title, "Latin-ASCII"),
           Title = str_remove(Title, " // .*"), 
           Title = str_remove(Title, "[^[:ascii:]].*"), 
           Title = str_trim(Title)) |>
    filter_out(Title == "") |>
    select(year, 
           period, 
           period_start, 
           period_end, 
           Title, 
           -half, 
           Runtime, 
           Views, 
           `Hours Viewed`, 
           `Release Date`,
           `Available Globally?`, 
           live_event) |>
    rename(title = Title,
           runtime = Runtime,
           views = Views,
           hours_viewed = `Hours Viewed`,
           release_date = `Release Date`,
           available_globally = `Available Globally?`) |>
    mutate(year = as.integer(year),
           available_globally = available_globally == "Yes")
}

NETFLIX_DATA <- load_netflix_data()
```

### Step 2/ Initial Data Exploration
Here, two functions will be used to get an idea of the data.

1. `glimpse()` - getting the basic dimensions of a data frame, printing a line summary of each column giving its name, type, and the first few values in the table
2. `skim()` - an overview about data structure and types, identifies grouping structure (if any is present), and gives summaries appropriate to the type of each column

*Note:* Also included, a render of `gt()`to experiment with the tool and to see how the data can be under an HTML table view. 

*1/ Using `glimpse()`*

```{r}
#| label: eda-glimpse
#| code-fold: false
glimpse(NETFLIX_DATA)
```

**Interpretation**

In this output, key information is given
- number of rows (to know how extensive the data is)
- number of columns (to see how many attributes there are per row)
- a line per row, giving the "name", the data type and the first few values for each

This is very useful, to envision on a high-level how the data frame is structured. Also, it is particularly useful to see each data type - as learned, R will interpret the data as structured in the data set. E.g. if year is a chr (a "string"), R will consider it as such, even though a human knows that year is composed of integers. 

This "view" is used to introduce the data set, build the vision, and the foundations to after dig deeper into what to do with each values. Indeed, here the details that would serve for a proper "cleaning" are not enough. There are no descriptive statistics and information about NA values for example. 


*2/ Using `skim()`*
```{r}
#| label: eda-skim
#| code-fold: false
skim(NETFLIX_DATA)
```

**Interpretation**

Contrary to the `glimpse()`function, this output gives more granularity on the data. The same "basic information" appears (name, number of rows, number of columns) but what is interesting here is that this view focuses on variable types (character, date, logical and numeric). 

For each type, the name is given with additional information such as the number of NA and a full descriptive analysis (rate, mean, standard deviation, quartiles and a histogram). This is more useful when trying to understand the data set in a more statistical way, that can lead to an evaluation of what the output could be. However, since it tends more towards the statistical side, there are no overviews of the actual data (2023, 2023H1, period dates, title, runtime, views etc). 

As an ending note, the two functions serve two different purposes and are complementary. Each function can be used for a different purpose, and can serve better depending on the context and the data type. For example, if a data set is largely comprised of qualitative data, perhaps the `glimpse()`function would be more appropriate. And vice-versa.

*Additional optional step - `gt()`*\

The `slice_max()`method was chosen to ensure consistent output, with the 5 biggest title
```{r}
#| label: eda-gt-top5
NETFLIX_DATA |>
  slice_max(hours_viewed, n = 5) |>
  select(title, period, hours_viewed, views) |>
  gt() |>
  tab_header(title = "The 5 Netflix titles with the most Hours Viewed",
             subtitle = "From the WWW - What We Watched reports") |>
  cols_label(title = md("Title"),
             period = md("Period"),
             hours_viewed = md("Hours Viewed"),
             views = md("Views")) |>
  fmt_number(columns = c(hours_viewed, views),
             decimals = 0)
```


### Step 3/ Exploratory Questions




### Step 4/ Exploratory Tables



### Step 5/ Strategy Memo (with visualization)




### AI Usage Statement




